\bf Faster Neural Machine Translation Inference

### 2018-01-30 fast-beam/fast-beam.tex
begin matrix wrapper

We will look at two areas that are critical to fast NMT inference where the models in NMT differ significantly from those in other applications. These areas have been overlooked by the general deep-learning community, we aim to improve their efficient for NMT-specific tasks.

@@

Secondly, the use of mini-batching is critical for fast model inference. However, mini-batching does not take into acccount variable sentence lengths which decrease the actual number of input or output sentences that are processed in parallel, negating the benefit of mini-batching. This can be partially reduced in the encoding with \emph{maxi-batching}, i.e. pre-sorting sentences by length before creating mini-batches with similar length source sentences. However, target sentence lengths will still differ even for similar length inputs, compromising decoding performance. Figure~\ref{fig:batch-size} shows the actual batch size during decoding with a maximum batch size of 128; in only 42\% of decoding iteration was batch full.

@@

We base our model on the sequence-to-sequence model of ~\cite{D14-1179} for machine translation models and also choose to focus on the using GPUs rather than CPUs as pursued by ~\cite{DBLP:conf/emnlp/Devlin17}.

@@

>>>>

We will examine two areas that are critical to fast NMT inference where the models differ significantly from other deep-learning models. We believe the optimizations of these models have been overlooked by the general deep-learning community.

@@

Secondly, the use of mini-batching is critical for fast model inference. However, mini-batching does not take into acccount variable sentence lengths which decrease the actual number of input or output sentences that are processed in parallel, negating the benefit of mini-batching. This can be partially reduced in the encoding with \emph{maxi-batching}, i.e. pre-sorting sentences by length before creating mini-batches with similar length source sentences. However, target sentence lengths will still differ even for similar length inputs, compromising decoding performance. Figure~\ref{fig:batch-size} shows the actual batch size during decoding with a maximum batch size of 128; the batch was full in only 42\% of decoding iterations.

@@

We base our work on the sequence-to-sequence model of ~\cite{D14-1179}. We also choose to focus on the using NMT inference on GPUs. % rather than CPUs as pursued by ~\cite{DBLP:conf/emnlp/Devlin17}.

@@

REDO
